---
title: "Week Two Unit 2 Part 4"
author: "Weijia Chen"
date: "23 September 2014"
output: html_document
---

```{r, results='hide', echo=FALSE}
options(scipen = 1)
```

###Binomial Distribution

####Definition,properties, conditions

The $binomial\ distribution$ describes the probability of having exactly $k$ successes in $n$ **_independent_**Bernouilli trials with the probability of success $p$

$$number \ of\ scenarios * P(single \ scenario)$$

$P(single \ scenario) = p^k (1-p) ^{(n-k)}$

$p^k$ is the probability of success to the power of number of success

$(1-p)^{(n-k)}$ is the probability of failure to the power of number of failures.

#####n choose r
How many scenarios can be calculated by:
$$\displaystyle \binom{n}{r} = \frac{n!}{k!(n-k)!}$$

In R:

`choose()`is the funciton to calculate the scenarios
```{r}
choose(9,2)
```

####Calculating probabilities

If $p$ represents probability of success, $(1-p)$ represents probability of failure, $n$ represents number of independent trials, and $k$ represents number of success,

$$P(k \ successes \ in \ n \ trials) = \displaystyle \binom{n}{r} p^k (1-p)^{(n-k)}$$

Where $\displaystyle \binom{n}{r} = \frac{n!}{k!(n-k)!}$

In R, `dbinom()` function can calculate the binomial probability

```{r}
dbinom(8, size = 10, p = 0.13)
```

#####Binomial Conditions

1. The trials must be independent
2. The number of trails, $n$, must be fixed
3. Each trial outcome must be classified as success or a failure
4. The probability of success, $p$, must be the same for each trial

####Mean and standard deviation

Expected value (mean) of binomial distribution: $\mu = np$

Standard deviation of binomial distribution: $\sigma = \sqrt{np(1-p)}$

###Normal Approximation to Binomial

Success-failure rule: A binomial distribution with at least 10 expected successes and 10 expected failures closely follows a normal distribution.

$np \geq 10$

$n(1-p) \geq 10$

Normal approximation to the binomial: If the success-failure condition holds,

$$Binomial(n,p) \sim Normal(\mu, \sigma)$$

Where $\mu = np$ and $\sigma = \sqrt{np(1-p)}$
